Capstone Movielens Report

### 2025-11-14 reports/capstone-movielens.site/05.appendix.Rmd
Minor fixes for functions' descriptions related to k-fold cross-validation.

This function produces datasets listed in the [Value](#func.make_source_datasets.value) section below and described in detail in [Appendix B: Models Training Datasets] using the `edx` as the original dataset.

@@

::: { #func.union_cv_results.args.data_list .sidebar }
  - **data_list:** List of data frames representing the results of the *K-Fold Cross-Validation* method execution.;

::: { #func.union_cv_results.details .sidebar }
##### Details
\
This function internally uses the [base::union](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/sets) `R` function to combine the data from the list of data frames (result of the *K-Fold Cross-Validation*) passed in the [data_list] argument into a single data frame for further processing.
:::

@@

The Mean Squared Errors (MSEs) values obtained from applying the *K-Fold Cross-Validation* method to the *Overall Average Rating (OMR) Model*, where the `K` value is determined by the length of the [`edx_CV` Object].

@@

Calculates *Mean Squared Error (MSE)* for the *UM Effect (UME) Model* produced by the  [train_user_movie_effect](#func.train_user_movie_effect) or [train_user_movie_effect.cv](#func.train_user_movie_effect.cv) function call.

@@

To calculate the *MSE* for the *UME Model* passed in the [um_effect](#func.calc_user_movie_effect_MSE.args.um_effect) argument, the function uses the validation dataset passed in the [test_set](#func.calc_user_movie_effect_MSE.args.test_set) arg.

@@

@@

The function calculates *RMSE* for the *UME Model* passed in the [um_effect](#func.calc_user_movie_effect_RMSE.cv.args.um_effect) argument using the validation datasets contained in the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets].

@@

The *RMSE* value calculated for the *UM Effect Model* using the *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object].
:::

>>>>

This function produces datasets listed in the [Value](#func.make_source_datasets.value) section below and described in detail in [Appendix B: Models Training Datasets], using the `edx` as the original dataset.

@@

::: { #func.union_cv_results.args.data_list .sidebar }
  - **data_list:** List of data frames representing the results of the *K-Fold Cross-Validation* method execution.

::: { #func.union_cv_results.details .sidebar }
##### Details
\
This function internally uses the [base::union](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/sets) `R` function to combine the data from the list of data frames (result of the *K-Fold Cross-Validation*) passed in the [data_list](#func.union_cv_results.args.data_list) argument into a single data frame for further processing.
:::

@@

The Mean Squared Error (MSE) values obtained from applying the *K-Fold Cross-Validation* method to the *Overall Average Rating (OMR) Model*, where the `K` value is determined by the length of the [`edx_CV` Object].

@@

Validates the *UM Effect (UME) Model* produced by the  [train_user_movie_effect](#func.train_user_movie_effect) or [train_user_movie_effect.cv](#func.train_user_movie_effect.cv) function call.

@@

The function calculates *Mean Squared Error (MSE)* for the *UME Model* passed in the [um_effect](#func.calc_user_movie_effect_MSE.args.um_effect) argument using the validation dataset passed in the [test_set](#func.calc_user_movie_effect_MSE.args.test_set) arg.

@@

The `K` value for the *K-Fold Cross-Validation* is determined by the length of the [`edx_CV` Object].
:::
:::

@@

The function calculates *Root Squared Error (RMSE)* for the *UME Model* passed in the [um_effect](#func.calc_user_movie_effect_RMSE.cv.args.um_effect) argument using the validation datasets contained in the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets].

@@

The *RMSE* value calculated for the *UM Effect Model* with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object].
:::
